---
title: "Satelite Imagery data"
author: "Nikola Geršak"
date: "2022-07-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(sen2r)
```

The data I obtained from the first rmd document concerns the inventory of forests. In the second step, I would like to correlate this data with the satellite data from the copernicus's sentinell 2 satelite and see where this will take me. I suppose this process can be separated in few steps I can think of:

<ol>

get the satellite images from sentinel 2 
calculate the vegetation indices
merge the inventory data with the indices by points that represent geolocations
draw some graphs
predict the biomass of the rest of Medvednica, or the tree types, or species distribution 
</ol>



## Obtaining the satellite images of the area {-}

I will get them with the help of sen2r library

```{r}
s2_list() #to retrieve the list of available Sentinel-2 products based on input parameters;
s2_download() #to download Sentinel-2 products;
s2_order()
```

## Vegetation indices {-}

```{r}
library(raster)
#raslist <- paste0('data/rs/LC08_044034_20170614_B', 1:11, ".tif")
sentinell <- stack(raslist)

vi <- function(img, k, i) {
  bk <- img[[k]]
  bi <- img[[i]]
  vi <- (bk - bi) / (bk + bi)
  return(vi)
}

ndvi <- vi(sentinell, 5, 4)
plot(ndvi, col = rev(terrain.colors(10)), main = "Sentinell-NDVI")

#extract from raster to get the ndvi values for points and merge them with specified points
extract(ndvi)

```

# Correlation {-}

After merging the vegetation indices with inventory data I can correlate it as well as to do the PCA, lm, glm etc.
